---
title: "Comparision of Corona Infection Cases of Nepal With Countries Recovered From Infections"
output:
  html_document: default
  pdf_document: default
---
R.K.Mallik,
Phd Candidate, Civil Engineering
IOE, Pulchowk Campus
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### Summary

Nepal is compared with other 18 countries recovered from corona infection.
We can clearly see three types of recover pattern.
Comparing with these three recovering pattern gives some useful insight that can help to estimate maximum possible corona case in Nepal.

### Import the Important Library

```{r import libraries}
library(plotly)
library(TTR)
library(tidyr)
library(dplyr)
library(ggplot2)
```

### Reading Data

```{r read csv file}
coronaWorldData<-read.csv(file = "owid-covid-data3.csv") # From Our World with data
data1<-data.frame(coronaWorldData)
data1[is.na(data1)]<-0
names(data1)
data1$date<-as.Date(data1$date)
```

### Selecting Important features

Data has in total 32 features out of which 8 features has been selected for the analysis for this time the two features has been presented 

+ new_cases_per_million 
+ total_cases_per_million

The population of the countries are normalized to 1 Million so that we can logically compare seviarity of the virus spreading 
```{r}
features<-c("location","date","new_cases","total_cases","new_deaths",
            "total_deaths","new_cases_per_million","total_cases_per_million","population_density")
```

### Subset data for analysis

Subset of the data is collected as per the selected features.
```{r}
data_features<-data1[,features]
names(data_features)

```


### Collective plot of different countries

17 Countries that have controlled corona virus outbreaks are selected. Three groups are made based up on the performance of country controlling virus spreading

+Group 1: Country with well performance
+Group 2: Country with lots of struggle but controlled the virus spreding
+Group3: Country controlled viruse passing through worst possible virus spreading


```{r}
contrlCountry1<-c("Australia","Nepal","India","South Korea","Japan") # Group 1
contrlCountry2<-c("Germany","Denmark","Nepal","India","Turkey","France","Netherlands") # Group 2"Austria","Norway",
contrlCountry3<-c("Nepal","India","Italy","Spain","Iceland","Switzerland","Belgium","United Kingdom") # Group 3

contrlData1<-data_features%>%filter(location == contrlCountry1)
contrlData2<-data_features%>%filter(location == contrlCountry2)
contrlData3<-data_features%>%filter(location == contrlCountry3)
countryData_nep_ind<-data_features%>%filter(location == c("Nepal","India"))
```
### Comparing Nepal and India Daily New case 
```{r}
ggplot(data=countryData_nep_ind,aes(group=location))+
  geom_line(aes(x=date,y=new_cases_per_million,color=location))+
  scale_shape(solid=FALSE)+
  ggtitle(" Comparision of Nepal With Countries With Best Control on Virus Spreading")+
  xlab("Expected Total cases for Nepal = 7,275 (BEST PERFORMANCE REQUIRED)")+
  ylab("Total Infection Cases Per Million")+
  theme(axis.text.x=element_text(angle=90,hjust=1))

```






### Comparing Nepal and India case with Better performing countries

```{r}
ggplot(data=contrlData1,aes(group=location))+
  geom_line(aes(x=date,y=total_cases_per_million,color=location))+
  scale_shape(solid=FALSE)+
  ggtitle(" Comparision of Nepal With Countries With Best Control on Virus Spreading")+
  xlab("Expected Total cases for Nepal = 7,275 (BEST PERFORMANCE REQUIRED)")+
  ylab("Total Infection Cases Per Million")+
  theme(axis.text.x=element_text(angle=90,hjust=1))

#n = M/(1+M*exp(-c*factor(contrlCountry1$date)))

```
### FITTING WITH SIGMOID FUNCTION BY R.K.Mallik
```{r}
countryAustralia<-c("Australia") # Group 1
contrlAustralia<-data_features%>%filter(location == countryAustralia)
contrlAustralia1<-contrlAustralia[contrlAustralia$total_cases_per_million>1,]
contrlAustralia1$total_cases_per_million
M = max(contrlAustralia1$total_cases_per_million)# Saturation value
t<-1:length(contrlAustralia1$total_cases_per_million)
err=NULL
for (i in 1:100){
  c = 0.01*i
  n = M/(1+M*exp(-c*t))
  sq = (n-contrlAustralia1$total_cases_per_million)**2
  err[i] = mean(sqrt(sq))
}
c1=which(err==min(err))*0.01
c1
n1 = M/(1+M*exp(-c1*t))

contrlAustralia1$pred<-n1

ggplot(data=contrlAustralia1)+
  geom_line(aes(x=date,y=total_cases_per_million,color="observations"))+
  geom_line(aes(x=date,y=pred,color="sigmoid_fitted"))+
  scale_shape(solid=FALSE)+
  ggtitle(" Sigmoid Curve Fitting for cumulative daily cases")+
  xlab("Date")+
  ylab("Cumulative Cases")+
  theme(axis.text.x=element_text(angle=90,hjust=1))



```
### SIGMOID FITTING FOR THE JAPAN BY R.K.Mallik
```{r}
countryJapan<-c("Japan") # Group 1
contrlJapan<-data_features%>%filter(location == countryJapan)
contrlJapan1<-contrlJapan[contrlJapan$total_cases_per_million>1,]
contrlJapan$total_cases_per_million
contrlJapan1$total_cases_per_million
M = max(contrlJapan1$total_cases_per_million)# Saturation value
M
t<-1:length(contrlJapan1$total_cases_per_million)
k=1
for (i in 1:100){
  c = 0.01*i
  n = M*(1-exp(-c*t))/(1+k*M*exp(-c*t))
  sq = (n-contrlJapan1$total_cases_per_million)**2
  err[i] = mean(sqrt(sq))
}
c1=which(err==min(err))*0.01
c1
n1 = M*(1-exp(-c1*t))/(1+M*exp(-c1*t))

contrlJapan1$pred<-n1

ggplot(data=contrlJapan1)+
  geom_line(aes(x=date,y=total_cases_per_million,color="observations"))+
  geom_line(aes(x=date,y=pred,color="sigmoid_fitted"))+
  scale_shape(solid=FALSE)+
  ggtitle(" Sigmoid Curve Fitting for cumulative daily cases")+
  xlab("Date")+
  ylab("Cumulative Cases")+
  theme(axis.text.x=element_text(angle=90,hjust=1))

```


### SIGMOID FITTING FOR THE NEPAL
### Reading Data of Nepal
```{r}
coronaCasesNepal<-read.csv(file = "coronaNepal1.csv")
data1<-data.frame(coronaCasesNepal)
str(data1)
y<-data1$NewCases
total_cases<-cumsum(y)
total_cases_pm<-total_cases/29.1
data1$total_pm<-total_cases_pm
data1$total_pm
```

```{r}
contrlNepal1<-data1[data1$total_pm>1,]
contrlNepal1$total_pm
date<-contrlNepal1$Date
Nepal_ts<-ts(contrlNepal1$total_pm,frequency = 1)
t = 1:length(contrlNepal1$total_pm)
c3 = 0.09
t1 = 37
y1 = 30.206186
n1 = 1/(1/y1+exp(-c3*t)-exp(-c3*t1))
n1_ts<-ts(n1,frequency = 1)
contrlNepal1$pred<-n1
ggplot(data=contrlNepal1)+
  geom_line(aes(x=date,y=total_pm,color="total_pm"))+
  geom_line(aes(x=date,y=pred,color="sigmoid_fitted"))+
  scale_shape(solid=FALSE)+
  ggtitle(" Sigmoid Curve Fitting for cumulative daily cases")+
  xlab("Date")+
  ylab("Cumulative Cases")+
  theme(axis.text.x=element_text(angle=90,hjust=1))
ts.plot(Nepal_ts,n1_ts,
        gpars=list(main = "CoronaSigmoidFunction Fitted With Nepal Cumulative Case",xlab="Date Count From 21st April",ylab="Cumulative Infection",lty=c(1,6)))
Nepal_ts
n1_ts
```

```{r}
require(graphics)
x = 1:200
c3 = 0.10101
t1 = 46
y1 = 99.862543
n2 = 1/(1/y1+exp(-c3*x)-exp(-c3*t1))
n2_ts<-ts(n2,frequency=1)
ts.plot(Nepal_ts,n2_ts,
        gpars=list(main = "CoronaSigmoidFunction Fitted With Nepal Cumulative Case",xlab="Date Count From 21st April",ylab="Cumulative Infection",lty=c(1,6)))
n2_ts
```

```{r}
M = 500
x = 1:100
c3 = 0.1
n2 = 1/(1/M+exp(-c3*x))
plot(x,n2)
```


### Comparing Nepal and India case with Just good performing countries

```{r}
ggplot(data=contrlData2,aes(group=location))+
  geom_line(aes(x=date,y=total_cases_per_million,color=location))+
  scale_shape(solid=FALSE)+
  ggtitle(" Comparision of Nepal With Countries With good control on virus spreading")+
  xlab("Expected Total cases for Nepal = 65,475 (POSSIBLE WITH BETTER PLANNING)")+
  ylab("Total Infection Cases Per Million")+
  theme(axis.text.x=element_text(angle=90,hjust=1))

```
```{r population density}
ggplot(data=contrlData2,aes(group=location))+
  geom_histogram(aes(x=population_density,color=location))+
  scale_shape(solid=FALSE)+
  ggtitle(" Comparision of Nepal With Countries With good control on virus spreading")+
  xlab("Expected Total cases for Nepal = 65,475 (POSSIBLE WITH BETTER PLANNING)")+
  ylab("Total Infection Cases Per Million")+
  theme(axis.text.x=element_text(angle=90,hjust=1))
```
### Comparing Nepal and India case with worst performing controlled countries

```{r}
ggplot(data=contrlData3,aes(group=location))+
  geom_line(aes(x=date,y=total_cases_per_million,color=location))+
  scale_shape(solid=FALSE)+
  ggtitle(" Comparision of Nepal With Countries Recovered From Worst Virus Spreading Case")+
  xlab("Expected Total cases for Nepal = 1,45,500 (POSSIBLE WITH GOOD PLANNING WITH HARD TIME)")+
  ylab("Total Infection Cases Per Million")+
  theme(axis.text.x=element_text(angle=90,hjust=1))

```
```{r}
ggplot(data=contrlData3,aes(group=location))+
  geom_histogram(aes(x=population_density,color=location))+
  scale_shape(solid=FALSE)+
  ggtitle(" Comparision of Nepal With Countries Recovered From Worst Virus Spreading Case")+
  xlab("Expected Total cases for Nepal = 1,45,500 (POSSIBLE WITH GOOD PLANNING WITH HARD TIME)")+
  ylab("Total Infection Cases Per Million")+
  theme(axis.text.x=element_text(angle=90,hjust=1))

```

### FITTING WITH SIGMOID FUNCTION
```{r}
contrlData1
total_per_million<-contrlData1$total_cases_per_million
total_case_ts<-ts(total_per_million,frequency=1)
x<-0:300
theta = 0.01
alpha = 0.05
y = M/(1+alpha*exp(-theta*x))
plot(y~x)

```






### CONCLUSION FROM THE COMPARISION

Grouping 18 countries as per their performance in cotrol for the spreading of corona virus, we can expect Nepal beahave similar.

+ With the best possible planning for controlling spread of corona virus expected maximum corona virus case will be approximately : 7,225 No { Min = 6,550 & Max = 8,000 }
+ With the better planning for controlling spread, Expected corona infection case:65,475 No. { Min = 52,380, Max = 80,025}
+ With just good planning and controlling mechanism, Expected corona infection case:1,45,500 {min = 1,01,850 & Max = 1,54,230}

### LIMITATIONS OF THESE COMPARISION

+ The immunity power of all the persions are assumed as similar
+ The population density has major impacts as it causes automatic social distancing and it has been grouped as 3 nos only. Its effect can be seen through deep learning techniques and it is under study.
+ All the people in the societies are not vaccined and equally succeptible for the infection.
